---
title: "Tutorial 6: Refactoring R Code"
---

# Introduction

In this tutorial, you will refactor the code into separate scripts corresponding to each section. The dataset we will use comes from the `palmerpenguins` package, which contains measurements of penguins from three species.

## Load Libraries and Data

```{r}
#| echo: fenced
# Run "01_load_data.R"
clean_data <- readr::read_csv("data/penguin_clean.csv")
head(clean_data)
```

# Methods

In this section, we perform exploratory data analysis (EDA) and prepare the data for modeling.

```{r}
# Run "02_methods.R"
modelready_data <- readr::read_csv("data/penguin_modelready.csv")
head(modelready_data)
```

# Model

We will fit a classification model using `tidymodels` to predict the species of a penguin based on its physical characteristics.

```{r}
# Run "03_model.R"
penguin_fit <- readr::read_rds("output/penguin_fit.RDS")
summary(penguin_fit)
```

# Results

We evaluate the performance of the model using the test dataset.

```{r}
# Run "04_results.R"
conf_mat <- readr::read_rds("output/conf_mat.RDS") 
conf_mat
```

# Conclusion

In this tutorial, we:

- Loaded and cleaned the `palmerpenguins` dataset.
- Performed exploratory data analysis.
- Built a k-Nearest Neighbors classification model using `tidymodels`.
- Evaluated the model's performance.
